\LaTeX\ Author Guidelines for 3DIMPVT Proceedings

### 2012-06-19 3dimpvt/paperv1.tex
about to kill a bunch of old text from v1

\subsection{Occlusion Checking}
Before we proceed with texturing our planes, we need to ensure that
each plane's associated images contain only content that should be
mapped onto the target plane in question. From the above process,
images were chosen such that they had an unoccluded view of one or
more trianglular sections upon a plane. This may not necessarily hold
true however for all areas of the plane, as demonstrated in figure
SOMETHING. If images are not modified to mask out occluded areas,
different images could attempt to cover the same location on a plane
with drastically different textures, inevitably leading to
undesireable discontinuities in our final texture.

@@

\section{Our Approach Overview}
Our approach begins 
with the projection of all our images onto
separate copies of our plane, such that no projected data is covered
and lost. Tis is done by discretizing the plane into an arbitrary density of points, and projecting each point into the image plane using the camera matrix $P_i$. We then perform a series of preprocessing steps to rotate
and shift each image's projection such that its overlapping regions
with other projections are as seamless as possible. From here, we assign textures to our planes
using one of two methods, dependent on whether they are wall planes or
ceiling/floor planes. The reasoning for this is explained in section
\ref{sec:whydifferent}. Lastly, we apply two post-processing steps to smooth out
any remaining seams.

>>>>

\subsection{Occlusion Masking}
Before we proceed with texturing our planes, we need to ensure that
each plane's associated images contain only content that should be
mapped onto the target plane in question. From the above process,
images were chosen such that they had an unoccluded view of one or
more trianglular sections upon a plane. This may not necessarily hold
true however for all areas of the plane, as demonstrated in figure
SOMETHING. If images are not modified to mask out occluded areas,
different images could attempt to cover the same location on a plane
with drastically different textures, inevitably leading to
undesireable discontinuities in our final texture.

@@

\section{Our Approach}
Our approach begins 
with the projection of all our images onto
separate copies of our plane, such that no projected data is covered
and lost. Tis is done by discretizing the plane into an arbitrary density of points, and projecting each point into the image plane using the camera matrix $P_i$. We then perform a series of preprocessing steps to rotate
and shift each image's projection such that its overlapping regions
with other projections are as seamless as possible. From here, we assign textures to our planes
using one of two methods, dependent on whether they are wall planes or
ceiling/floor planes. The reasoning for this is explained in section
\ref{sec:whydifferent}. Lastly, we apply two post-processing steps to smooth out
any remaining seams.
